%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
 \usepackage[sfdefault]{sans} % well readable

% serif
 %\usepackage{charter} % fancy


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

% \urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\definecolor{GoogleGreen}{RGB}{60, 186, 84}
\definecolor{GoogleYellow}{RGB}{244, 194, 13}
\definecolor{GoogleBlue}{RGB}{72, 133, 237}
\definecolor{GoogleRed}{RGB}{219, 50, 54}
\newcommand{\GoogleLogo}{{\textcolor{GoogleBlue}{G}\textcolor{GoogleRed}{o}\textcolor{GoogleYellow}{o}\textcolor{GoogleBlue}{g}\textcolor{GoogleGreen}{l}\textcolor{GoogleRed}{e}}}

%\usepackage{hyperref}% http://ctan.org/pkg/hyperref
% \hypersetup{
%   colorlinks=true,
%   linkcolor=blue!50!red,
%   urlcolor=green!70!blue
% }

\usepackage{hyperref}
\hypersetup{
    colorlinks = true,
    linkcolor=blue!50!red,
    urlcolor=[RGB]{29, 68, 128}
}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
    \textbf{\Huge \scshape Lukas Scheucher} \\ \vspace{1pt}
%     \small <<phone>> $|$ \href{mailto:lukas@scheuclu.com}{\underline{lukas@scheuclu.com}} $|$
    \href{mailto:lukas@scheuclu.com}{\underline{lukas@scheuclu.com}} $|$
    % \href{https://linkedin.com/in/<<linkedin>>}{\underline{linkedin.com/in/<<linkedin>>}} $|$
    \href{https://github.com/scheuclu}{\underline{github.com/scheuclu}} $|$
    \href{https://scheuclu.com}{\underline{scheuclu.com}}
\end{center}



%-------------------------------------------

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Post Graduate Researcher }{Jul 2017 -- Jun 2018}
      {Munich}{Germany}
    \resumeItemListStart
      \resumeItem{Uncertainty quantification in physical simulations using bayesian methods and machine learning}
      \resumeItem{Design optimization. Collaborative development of a C++ HPC codebase.}
    \resumeItemListEnd
    \resumeSubheading
      {M.Sc. Mechanical Engineering }{Oct 2012 -- Jun 2017}
      {TUM}{Munich}
    \resumeItemListStart
      \resumeItem{Majored in Computational Engineering and High Performance Computing.}
      \resumeItem{Visiting Researcher at Stanford University}
    \resumeItemListEnd
    \resumeSubheading
      {Professional Certifications }{ -- }
      {Online}{Multiple}
    \resumeItemListStart
      \resumeItem{Total of 16 professional certifications including}
      \resumeItemListStart
        \resumeItem{\href{https://confirm.udacity.com/PRDLGCYP}{Blockchain Developer Nanodegree - Udacity}}
        \resumeItem{\href{https://coursera.org/share/ec095b18337aecea2c101552eeb97dd3}{5-part deep learning specialization -  Deeplearning.ai}}
        \resumeItem{\href{https://coursera.org/share/0be4aacea173ecab67e917e79c1ae954}{Decentralized finance - Duke University}}
        \resumeItem{\href{https://www.linkedin.com/in/scheuclu}{Full list on LinkedIn}}
      \resumeItemListEnd
    \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Freelance Software Engineer }{May 2022 -- present}
      {Toptal}{Remote}
    \resumeItemListStart
      \resumeItem{Working as a freelance engineer on projects focusing on data-science and backend engineering.}
      \resumeItem{Using my free time to develop an app on the side.}
    \resumeItemListEnd
    \resumeSubheading
      {Founder in Residence }{Mar 2022 -- May 2022}
      {Enterpreneur First}{London}
    \resumeItemListStart
      \resumeItem{I was accepted into the 2022 cohort and spent 2 months working with dedicated individuals on blockchain/web3 ideas.}
      \resumeItem{Unfortunately, I did not find the right co-founder/idea.}
    \resumeItemListEnd
    \resumeSubheading
      {Software Engineer }{Nov 2019 -- Dec 2021}
      {Google}{Munich}
    \resumeItemListStart
      \resumeItem{Using data analysis on production logs to improve reliability across Google. Used tensorflow, Go and Apache flume}
      \resumeItem{Came up with an lead an successful internal project combining data analysis and visualization.}
      \resumeItem{ \textbf{X, the moonshot factory:} Data analysis on an experimental wearable device. Owned whole python codebase and training pipeline.}
    \resumeItemListEnd
    \resumeSubheading
      {Deep/Machine Learning Engineer }{Jul 2018 -- Oct 2019}
      {Volkswagen}{Munich}
    \resumeItemListStart
      \resumeItem{Worked as an applied machine learning engineer, mainly on computer vision for autonomous driving.}
      \resumeItem{Real time object detection, Model development, training, selection, compression and testing.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Research Work}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Post Graduate Work }{Jul 2017 -- Jun 2018}
      {TUM}{Munich}
    \resumeItemListStart
      \resumeItem{Uncertainty quantification in physical simulations using bayesian methods and machine learning.}
      \resumeItem{Design optimization under uncertainty.}
      \resumeItem{Collaborative development of a C++ research code (Full CI/CD pipeline).}
      \resumeItem{Visualization of complex simulation output using Paraview, Plotly, D3.js, ...}
      \resumeItem{Held several positions as teaching assistant.}
    \resumeItemListEnd
    \resumeSubheading
      {Visiting Graduate Researcher }{Oct 2016 -- Jul 2017}
      {Stanford University}{California}
    \resumeItemListStart
      \resumeItem{Implemented gradient computation in a C++ fluid dynamics \href{https://bitbucket.org/frg/aero-f/src/master/}{code}}
      \resumeItem{Application: Parametric shape optimization of flexible wings.}
      \resumeItem{Audited Stanford lecture series on machine learning by Andrew Ng.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{ \textbf{Blockchain}: Bitcoin, Ethereum, Solidity, web3.js, Smart-Contracts}
    \resumeItem{ \textbf{Languages}: Python, C++, Solidity, Go, SQL, Javascript, Bash}
    \resumeItem{ \textbf{Developer Tools}: Git, Docker, Google Cloud Platform, VIM, IntelliJ}
    \resumeItem{ \textbf{Libraries}: Tensorflow, Pytorch, OpenMP, MPI, CUDA, Pandas, NumPy, Matplotlib, Plotly, Dash}
    \resumeItem{ \textbf{Machine Learning}: Computer Vision, Recurrent Networks, Deep Learning, Model training and selection. Model compression.}
  \resumeItemListEnd


%-------------------------------------------
\end{document}
